---
title: "MICR AXB Combined Analysis"
output: html_notebook
---
# Set up
## Packages
```{r, warning=F}
# Wrangling
library(tidyverse)
library(mgsub)

# Statistics/Numerical processing
library(brms)
library(lme4)
library(boot)

# PCA
library(FactoMineR) 
library(factoextra) 
library(GPArotation)
library(paran)

# Plotting
library(ggplot2)
library(ghibli)

# Optional settings
options(dplyr.summarise.inform=F) # Stop dplyr from printing summarise error (that isn't an error)
select <- dplyr::select # Ensure that select() command is the dplyr command (clashes with MASS, which is imported/required by paran)
```

## Functions
```{r, warning=F}
# Standard error function
std.error <- function(x, na.rm = T) {
  sqrt(var(x, na.rm = na.rm)/length(x[complete.cases(x)]))
}

# general standardized ggplot theme
gg_theme <- function() {
  theme_bw() +
  theme(plot.title=element_text(size=25),
        plot.subtitle=element_text(size=15, face="italic"),
        axis.title=element_text(size=20),
        axis.text=element_text(size=15),
        strip.background =element_rect(fill="white"),
        strip.text = element_text(size=15))+
  theme(legend.title = element_text(size=15, face="bold"),
        legend.text=element_text(size=15))
}

# color theme for guise plots
guise_colors <- function(gg_object, n_contrasts) {
  if (n_contrasts == 3) {
    col_values <- c(6,4,3)
  } else if (n_contrasts == 2) {
    col_values <- c(4,3)
  } else {
    return(print('Number of contrasts invalid: Must be either 3 or 2'))
  }
  
   return (
      gg_object +
        scale_fill_manual(values=ghibli_palette("PonyoMedium")[col_values])+
        scale_color_manual(values=ghibli_palette("PonyoMedium")[col_values])
    )
}

# color theme and labels for interaction plots
interaction_plot_theme <- function(gg_object, n_contrasts) {
    if (n_contrasts == 3) {
      col_values <- c(7,6,5)
  } else if (n_contrasts == 4) {
    col_values <- c(7,6,5,2)
  } else {
    return(print('Number of contrasts invalid: Must be either 3 or 4'))
  }
  return(
      gg_object +
        gg_theme() +
        scale_color_manual(values=ghibli_palette("MononokeMedium")[col_values])+
        scale_fill_manual(values=ghibli_palette("MononokeMedium")[col_values])+
        scale_shape_manual(values=c(16,15,17,18))+
        scale_linetype_manual(values=c("solid", "longdash", "dashed", "dotted"))+
        labs(y = 'Guise Effect', x = 'Stereotype Familiarity', 
             color = 'Empathy Quotient', fill = 'Empathy Quotient', 
             shape = 'Empathy Quotient', linetype = 'Empathy Quotient')
    )
}

## theme for pca plots
pca_plot_theme <- function(gg_object) {
  gg_object +
  gg_theme() +
  scale_x_continuous(lim=c(-3, 3),breaks=seq(-3,3,1)) +
  scale_y_continuous(lim=c(-3.5, 3.5),breaks=seq(-3,3,1)) +
  geom_hline(yintercept=0, linetype="dashed") +
  geom_vline(xintercept=0, linetype="dashed") +
  labs(x="Dim 1 (XX.X%)", y="Dim 2 (XX.X%)")
}

## theme for proportion plots
proportion_plot_theme <- function(gg_object) {
  gg_object %>% guise_colors(3) +
  gg_theme() +
  coord_cartesian(ylim=c(0, 1)) +
  scale_x_continuous(breaks = -3:3) +
  labs(y = "Proportion 'raised' response", x = "Continuum Step (UR to RS)", 
       color="Guise", fill="Guise", linetype = "Guise")
}
```

#...
# Combine Data
## Pre-Process Data

Get data from first data collection (1a) and second (1b). Merge processed questionnaire data with the processed AXB experiment data. (*NOTE: Removes any data that doesn't have data associated with the questionnaire*)
```{r}
### AXB Experiment 1a: Two Speakers, two guises
exp_1a <- read.csv('data/axb_1a_exp_data.csv', skipNul=T)
lbq_1a <- read.csv('data/axb_1a_lbq_data.csv', skipNul=T)

## Check number of participants
length(unique(exp_1a$participantId))
length(unique(lbq_1a$participantId))

## Merge data
(axb_1a <- exp_1a %>% merge(lbq_1a, .) %>%  mutate(experimentId = '1a') %>% relocate(experimentId))
```


```{r}
### AXB Experiment 1b: One Speaker, one guise
exp_1b <- read.csv('data/axb_1b_exp_data.csv', skipNul=T)
lbq_1b <- read.csv('data/axb_1b_lbq_data.csv', skipNul=T)

(axb_1b <- exp_1b %>% merge(lbq_1b, .) %>%  mutate(experimentId = '1b') %>% relocate(experimentId))
```

### Full Combined Dataset
```{r}
# All perception + questionanire data for speaker = S3 (sMich)
(axb_data <- axb_1a %>% rbind(., axb_1b) %>% filter(speaker=='S3') %>% select(-subject))
```

```{r}
# Each subject's questionnaire data (one row per subject)
(axb_bysubj <- axb_data %>% group_by(participantId) %>% filter(time_elapsed == min(time_elapsed)) %>% ungroup() %>%
   relocate(speakerGuise, .after=speakerOrder) %>%
   select(-tonesCorrect, -step:-ncol(.)))
```

Check the data to make sure everything is as expected.
```{r}
# Number of subjects
axb_bysubj %>% group_by(experimentId, speakerGuise) %>% summarize(count = n())

```

```{r}
colnames(axb_bysubj)
```

## Check Data (Interim)

```{r}
summary(axb_data)
```

```{r}
axb_bysubj %>% group_by(experimentId) %>% summarize(count = n(), meanEQ = mean(EQscore))
```

### Plots
#### Yes/No Questions
```{r}
# Overall total
yn_prop <-
axb_bysubj %>% mutate(EK3.CanAI = ifelse(EK3.CanAI==1, "yes", "no")) %>% count(EK3.CanAI) %>%
  pivot_wider(names_from = EK3.CanAI, values_from = n) %>% 
  mutate(prop.yes = yes/(yes+no))  %>%
  mutate(question="aiDiff") %>% relocate(question) %>%
  rbind(.,axb_bysubj %>% mutate(EK4.CanAU = ifelse(EK4.CanAU==1, "yes", "no")) %>% 
          count(EK4.CanAU) %>%
          pivot_wider(names_from = EK4.CanAU, values_from = n) %>% 
          mutate(prop.yes = yes/(yes+no))  %>%
          mutate(question="auDiff") %>% relocate(question)
  ) %>%
  rbind(.,axb_bysubj %>% mutate(EK1.CanSpeak = ifelse(EK1.CanSpeak==1, "yes", "no")) %>% 
          count(EK1.CanSpeak) %>%
          pivot_wider(names_from = EK1.CanSpeak, values_from = n) %>% 
          mutate(prop.yes = yes/(yes+no))  %>%
          mutate(question="speakDiff") %>% relocate(question)
  ) %>%
  rbind(.,axb_bysubj %>% mutate(EK2.CanPron = ifelse(EK2.CanPron==1, "yes", "no")) %>% 
          count(EK2.CanPron) %>%
          pivot_wider(names_from = EK2.CanPron, values_from = n) %>% 
          mutate(prop.yes = yes/(yes+no))  %>%
          mutate(question="pronDiff") %>% relocate(question)
  ) %>%
  
  ggplot(aes(y=prop.yes, x=question, color=question, label=round(prop.yes,2))) +
  geom_bar(aes(fill=question),stat="identity") +
  geom_label(nudge_y=-0.05) +
  scale_y_continuous(limits=c(0,1), breaks=seq(0,1,0.1)) +
  gg_theme() +
  labs(x="Question", y="Proportion 'yes'", color="Question") +
  theme(legend.position = "none")
yn_prop

ggsave(path="plots", filename="ynQues_prop.png", yn_prop, width=9, height=6, units = "in" , dpi=72)

```

#### Gender Distribution
```{r, warning=F }
# By ExperimentId
axb_bysubj %>% ggplot(aes(x=Gender, fill=Gender)) +
  geom_histogram(stat="count", alpha=0.8, na.rm=TRUE) +
  facet_grid(speakerGuise~experimentId) +
  scale_fill_manual(values=ghibli_palette("SpiritedMedium")[c(3,5,4)]) +
  gg_theme()

# Combined
axb_bysubj %>% ggplot(aes(x=Gender, fill=Gender)) +
  geom_histogram(stat="count", alpha=0.8, na.rm=TRUE) +
  facet_grid(speakerGuise~.) +
  scale_fill_manual(values=ghibli_palette("SpiritedMedium")[c(3,5,4)]) +
  gg_theme()

```

#### Score Distributions
##### EQ: Cog. Empathy
```{r, warning=F}
# By ExperimentId
axb_bysubj %>% ggplot(aes(x=EQscore,fill=speakerGuise,color=speakerGuise)) %>%
  guise_colors() +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count") +
  facet_grid(~experimentId)

# Combined Density
axb_bysubj %>% ggplot(aes(x=EQscore,fill=speakerGuise,color=speakerGuise))  %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count")

# Combined Boxplot
axb_bysubj %>% ggplot(aes(x=speakerGuise, y=EQscore)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE)

```

##### SA: Stereo. Awareness
```{r, warning=F}
# By ExperimentId
axb_bysubj %>% ggplot(aes(x=SAscore,fill=speakerGuise,color=speakerGuise)) %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count") +
  facet_grid(~experimentId)

# Combined Density
axb_bysubj %>% ggplot(aes(x=SAscore,fill=speakerGuise,color=speakerGuise))  %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count")

# Combined Boxplot
axb_bysubj %>% ggplot(aes(x=speakerGuise, y=SAscore)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE)

```

##### CE: Can. Experience
```{r, warning=F}
# By ExperimentId
axb_bysubj %>% ggplot(aes(x=CEscore,fill=speakerGuise,color=speakerGuise)) %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count") +
  facet_grid(~experimentId)

# Combined Density
axb_bysubj %>% ggplot(aes(x=CEscore,fill=speakerGuise,color=speakerGuise))  %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count")

# Combined Boxplot
axb_bysubj %>% ggplot(aes(x=speakerGuise, y=CEscore)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE)

```



## Dimensionality Reduction

### PCA: Awareness & Experience

```{r, eval=F}
# Check correlations, which motivate the use of PCA to reduce dimensionality
with(axb_bysubj, cor.test(IK2.ai, IK2.au))

# Test correlations of similar questions
with(axb_bysubj, cor.test(Travel.Can_Visits, Travel.Can_Time))
with(axb_bysubj, cor.test(SE1.Fam.oot_1, SE2.Freq.Overall_1))
with(axb_bysubj, cor.test(SE2.Freq.Overall_1, SE2.Freq.Recent_1))
with(axb_bysubj, cor.test(SE2.Freq.Overall_1, SE2.Freq.Child_1))
with(axb_bysubj, cor.test(SE2.Freq.Recent_1, SE2.Freq.Child_1))
```

#### Run PCA

Packages required for this PCA:
* `PCA` command from `FactoMineR` library (see index for more info)
* `paran` command from `paran` library
* `Varimax` command from `GPArotations` library (https://stats.stackexchange.com/questions/59213/how-to-compute-varimax-rotated-principal-components-in-r)

Packages for visualization of PCA
* `fviz_pca_ind` and `fviz_pca_biplot` from `factoextra` 

```{r lbqdata-pca2-prep}
# (0) Select data for PCA — only numerical columns
# names(axb_bysubj)

# Medium trimmed set — removes general Canadian stereotype experience/knowledge, imitation, Sources of CE, hockey
(quesdata.pca.med <- axb_bysubj %>% select(IK2.au, IK2.ai, 
                                          SE1.Fam.oot_1, SE2.Freq.Recent_1:SE2.Freq.Overall_1, 
                                          PE2.CanSpeakFreq.Recent_1:PE2.CanSpeakFreq.Overall_1,
                                          ME4.CanHearFreq.Recent_1:ME4.CanHearFreq.Overall_1))

```

```{r}
## (1) Run Parallel Analysis with `paran`
# Standard way to decide on the number of factors or components needed in an FA or PCA.
# Prints out a scree plot as well, with the randomized line + unadjusted line
paran(quesdata.pca.med,
      graph = TRUE, color = TRUE, 
      col = c("black", "red", "blue"), lty = c(1, 2, 3), lwd = 1, legend = TRUE, 
      file = "", width = 640, height = 640, grdevice = "png", seed = 0)
```

```{r, warning=F}
## (2) Run PCA with `FactoMineR`
# ncp = number of components; adjust after checking the parallel analysis output

# FactoMineR PCA Commands
#plbqPCA        # lists commands
#plbqPCA$var    # variables
#plbqPCA$ind    # individuals
#plbqPCA$call   # summary stats

lbqPCA <- PCA(quesdata.pca.med, scale.unit = T, ncp =2, graph=F)

## Relevant Raw PCA Output
# Eigenvalues & percent variance accounted for
(eigenvalues <- lbqPCA$eig)

# Eigenvectors (=Factor matrix, factor score coefficients; sometimes called the factor, but NOT factor scores)
eigenvectors <- lbqPCA$var$coord

# Factor loadings (eigenvectors scaled by the square root of their associated eigenvalues)
# Calculate factor loadings using the output eigenvectors and eigenvalues
rawLoadings <- sweep(lbqPCA$var$coord,2,sqrt(lbqPCA$eig[1:ncol(lbqPCA$var$coord),1]),FUN="/")

# Factor scores for each subject and dimension (also: Individual coordinate scores; principle coordinates)
rawScores <- lbqPCA$ind$coord

```

```{r}
## (3) Conduct rotation on the PCA factor loadings with `GPArotation`
# Rotations are typically done on the retained component factor loadings, not on all components nor on the eigenvectors
# Performed for ease of interpretation, maximizing factor loadings
(rotLoadings <- Varimax(rawLoadings)$loadings)

# Recover Rotation matrix from loadings
# Because the rotLoadings are calculated from rawLoadings %*% rotMatrix, can recover rotMatrix by rotLoadings "divided" by rawLoadings, which in matrix multiplication is multiplying by the inverse (transpose) 
# Note: For some reason, can't call Varimax(rawLoadings)$rotmat (just get NULL); this recreates the same matrix from Varimax(rawLoadings)
(rotMatrixL <- t(rawLoadings) %*% rotLoadings)

# Calculate rotated factor scores
# The formula simply multiplies the normalized variable scores with the rotation matrix to get rotated factor scores
# First, z-score the raw scores using base R scale()
# Then, matrix multiply the matrix of zScores with the rotation matrix
# Result is a matrix with columns=components and rows=each subject
zScores <- scale(rawScores)
rotScores <- zScores %*% rotMatrixL
```

#### Plot PCA
```{r}
## (4) Data Visualization of Raw Scores with `factoextra`

# Plot individual factor scores
fviz_pca_ind(lbqPCA, col.ind = "#00AFBB", repel = TRUE)

# Biplot, including individual scores and factor vectors
fviz_pca_biplot(lbqPCA, label = "all", col.ind = "#00AFBB", col.var="black", ggtheme = theme_minimal())
```

```{r}
## (5a) Manual Plots of Rotated Scores with `ggplot`

## Create dataframes of the rotated factor loading and factor score matrices
# Convert rotated factor loadings matrix to data frame; add variable number
rotLoadingsData <- as.data.frame(rotLoadings)
rotLoadingsData <- mutate(rotLoadingsData, variable = row.names(rotLoadings))
rotLoadingsData <- mutate(rotLoadingsData, variable = factor(variable))

# Convert rotated factor score matrix to data frame; add subject number
rotScoreData <- as.data.frame(rotScores)
rotScoreData <- rotScoreData %>% mutate(subject = 1:nrow(.))
```


```{r}
## (5b) Manual Plots of Rotated Scores with `ggplot`
## Create base plots
# Loading plot
rotLoadingsData %>% ggplot(aes(x=Dim.1, y=Dim.2)) %>%
  pca_plot_theme +
  labs(title="Variables - PCA") +
  geom_segment(data=rotLoadingsData, mapping=aes(x=0, y=0, xend=Dim.1*4, yend=Dim.2*4), arrow=arrow(), size=0.5, color="black") +
  geom_text(data=rotLoadingsData, aes(x=Dim.1*4, y=Dim.2*4, label=variable), color="red",check_overlap=T)

# Scatter plot of Individual factor scores
rotScoreData %>% ggplot(aes(x=Dim.1, y=Dim.2)) %>%
  pca_plot_theme +
  labs(title="Individuals - PCA") +
  geom_point(na.rm=TRUE, color="#00AFBB") +
  geom_text(aes(label=subject),hjust=1.5,vjust=1.5, color="#00AFBB", check_overlap=T)

## Merge loading and score plot = Biplot
# Biplot of factor loadings + ind factor scores
ggplot(rotScoreData, aes(x=Dim.1, y=Dim.2)) %>%
  # Theming
  pca_plot_theme +
  labs(title="Biplot - PCA") +
  # Individual plot
  geom_point(na.rm=TRUE, color="#00AFBB") +
  geom_text(aes(label=subject),hjust=1.5,vjust=1.5, color="#00AFBB", check_overlap=T)+
  # Overlay loading plot (i.e. arrows)
  geom_segment(data=rotLoadingsData, mapping=aes(x=0, y=0, xend=Dim.1*4, yend=Dim.2*4), arrow=arrow(), size=0.5, color="black") +
  geom_text(data=rotLoadingsData, aes(x=Dim.1*4.5, y=Dim.2*4.5, label=variable), color="red",check_overlap=T, nudge_y = 0)

```

#### Interpret PCA
```{r}
## Interpret PCs (Dimensions) based on factor loadings
rotLoadings.df <- as.data.frame(rotLoadings) %>%
  rownames_to_column(., "Variables") %>%
  rename(., "PC1"= "Dim.1", "PC2" = "Dim.2")
rotLoadings.df
```

```{r}
# PC1 Only Contributors
rotLoadings.df %>% filter(abs(PC1) > 0.2)
```


```{r}
# PC2 Only Contributors
rotLoadings.df %>% filter(abs(PC2) > 0.2)
```

```{r, warning=F}
# Check for overlapping contributors
rotLoadings.df %>% filter(abs(PC2) > 0.2 & abs(PC1) > 0.2)

# Check for non-contributors
rotLoadings.df %>% filter(abs(PC2) < 0.2 & abs(PC1) < 0.2)
```



### Finalize Results w/ PCA

```{r}
# For Merging: Convert rotated factor score matrix to data frame; add participantId (assuming order of input dataframe)
indPCAdata <- rotScoreData %>%
  mutate(participantId = axb_bysubj$participantId) %>%
  rename(CEscore_all = Dim.1) %>%
  rename(SAscore_all = Dim.2)

# Merge participant data with PC scores 
# Only select the main relevant scores
axb_subj_data <- axb_bysubj %>%
  merge(., indPCAdata) %>%
  mutate(MSscore_all = scale(SK2.MichvStand)) %>%
  mutate(EQscore_all = scale(EQ.raws)) %>%
  mutate_at(vars(Age), as.numeric) %>%
  mutate_if(is.character, as.factor) %>%
  select(-subject) %>%
  select(experimentId, participantId, conditionId, guiseCombination, speakerGuise, speakerOrder, Age, Gender, Ethnicity, CEscore_all, SAscore_all, MSscore_all, EQscore_all, everything())
  
# Check data
axb_subj_data
# summary(axb_subj_data)

# Write to file
# write.csv(axb_subj_data, 'data/axb_combined_subj_data.csv', row.names=F)

```

```{r}
axb_all_data <- axb_subj_data %>%
  merge(., axb_data)%>%
  relocate(CEscore_all:EQscore_all, .before=CEscore)

# summary(axb_all_data)
```

# ...
# Visualizations
## Summarize Data (Final)

### Score Plots
#### Score Distributions
##### EQ: Cog. Empathy
```{r, warning=F}
# Density By ExperimentId
axb_subj_data %>% ggplot(aes(x=EQscore_all,fill=speakerGuise,color=speakerGuise)) %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count") +
  facet_grid(~experimentId)

# Combined Density
axb_subj_data %>% ggplot(aes(x=EQscore_all,fill=speakerGuise,color=speakerGuise))  %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count")

# Boxplot By ExperimentId
axb_subj_data %>% ggplot(aes(x=speakerGuise, y=EQscore_all)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE) +
  facet_grid(~experimentId)

# Combined Boxplot
axb_subj_data %>% ggplot(aes(x=speakerGuise, y=EQscore_all)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE)

```

##### SA: Stereo. Awareness
```{r, warning=F}
# Density By ExperimentId
axb_subj_data %>% ggplot(aes(x=SAscore_all,fill=speakerGuise,color=speakerGuise)) %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count") +
  facet_grid(~experimentId)

# Combined Density
axb_subj_data %>% ggplot(aes(x=SAscore_all,fill=speakerGuise,color=speakerGuise))  %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count")

# Boxplot By ExperimentId
axb_subj_data %>% ggplot(aes(x=speakerGuise, y=SAscore_all)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE) +
  facet_grid(~experimentId)

# Combined Boxplot
axb_subj_data %>% ggplot(aes(x=speakerGuise, y=SAscore_all)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE)

```

##### CE: Can. Experience
```{r, warning=F}
# Density By ExperimentId
axb_subj_data %>% ggplot(aes(x=CEscore_all,fill=speakerGuise,color=speakerGuise)) %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count") +
  facet_grid(~experimentId)

# Combined Density
axb_subj_data %>% ggplot(aes(x=CEscore_all,fill=speakerGuise,color=speakerGuise))  %>%
  guise_colors(3) +
  gg_theme() +
  geom_density(alpha=0.3) +
  labs(title="", y="Count")

# Boxplot By ExperimentId
axb_subj_data %>% ggplot(aes(x=speakerGuise, y=CEscore_all)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE) +
  facet_grid(~experimentId)

# Combined Boxplot
axb_subj_data %>% ggplot(aes(x=speakerGuise, y=CEscore_all)) %>%
  guise_colors(3) +
  gg_theme() +
  # geom_violin(aes(fill = speakerGuise, color=speakerGuise), alpha=0.3, na.rm=TRUE) +
  geom_boxplot(aes(fill = speakerGuise, color=speakerGuise), width=0.5, alpha=0.3, na.rm=TRUE)

```

##### PCA Output Correlation

```{r}
pca_dist_plot <-
axb_subj_data %>% ggplot(aes(y=CEscore, x=SAscore)) %>% 
  pca_plot_theme() +
  theme(legend.position="bottom") +
  scale_x_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  scale_y_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  labs(y="CanEx Scores", x="StereoFam Scores", color="Participant Group", shape="Participant Group")+
  geom_point(na.rm=TRUE, size=5, alpha=0.5) +
  geom_smooth(method='lm', color="blue")
pca_dist_plot

ggsave(path="plots", filename="scores_CESA_distributions.png", pca_dist_plot, width=9, height=6, units = "in" , dpi=72)

```

```{r}
pca_dist_plot <-
axb_subj_data %>% ggplot(aes(y=EQscore, x=SAscore)) %>% 
  pca_plot_theme() +
  theme(legend.position="bottom") +
  scale_x_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  scale_y_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  labs(y="EQ Scores", x="StereoFam Scores", color="Participant Group", shape="Participant Group")+
  geom_point(na.rm=TRUE, size=5, alpha=0.5) +
  geom_smooth(method='lm', color="blue")
pca_dist_plot

ggsave(path="plots", filename="scores_EQSA_distributions.png", pca_dist_plot, width=9, height=6, units = "in" , dpi=72)
```


```{r}
pca_dist_plot <-
axb_subj_data %>% ggplot(aes(y=CEscore, x=SAscore)) %>% guise_colors(3) %>%
  pca_plot_theme() +
  theme(legend.position="bottom") +
  scale_x_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  scale_y_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  labs(y="CanEx Scores", x="StereoFam Scores", color="Participant Group", shape="Participant Group")+
  geom_point(aes(color=speakerGuise, shape=speakerGuise), na.rm=TRUE, size=5, alpha=0.7) +
  geom_smooth(method='lm', color="grey")
pca_dist_plot

# ggsave(path="plots", filename="PCA_distributions.png", pca_dist_plot, width=12, height=8, units = "in" , dpi=72)

# Add Marginal distributions
ggMarginal(pca_dist_plot, type = c("boxplot"), margins = c("both"), size=6, alpha=0.3, groupFill=TRUE, groupColour=TRUE)

pca_dist_plot_marg <-
ggMarginal(pca_dist_plot, type = c("density"), margins = c("both"), size=6, alpha=0.15, groupFill=TRUE, groupColour=TRUE)
pca_dist_plot_marg

ggsave(path="plots", filename="scores_CESA_distributions_density.png", pca_dist_plot_marg, width=9, height=8, units = "in" , dpi=72)

```

```{r}
score_cor <-
axb_subj_data %>% ggplot(aes(y=EQscore, x=SAscore)) %>% guise_colors(3) %>%
  pca_plot_theme() +
  theme(legend.position="bottom") +
  scale_x_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  scale_y_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  labs(y="EQ Scores", x="StereoFam Scores", color="Participant Group", shape="Participant Group")+
  geom_point(aes(color=speakerGuise, shape=speakerGuise), na.rm=TRUE, size=5, alpha=0.7) +
  geom_smooth(method='lm', color="grey")

score_cor_marg <-
ggMarginal(score_cor, type = c("density"), margins = c("both"), size=6, alpha=0.15, groupFill=TRUE, groupColour=TRUE)
score_cor_marg

ggsave(path="plots", filename="scores_EQSA_distributions_density.png", score_cor_marg, width=9, height=8, units = "in" , dpi=72)

```

```{r}
axb_subj_data %>% ggplot(aes(y=EQscore, x=CEscore)) %>% guise_colors(3) %>%
  pca_plot_theme() +
  theme(legend.position="bottom") +
  scale_x_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  scale_y_continuous(lim=c(-2.5, 2.5),breaks=seq(-3,3,1)) +
  labs(y="EQ Scores", x="CanEx Scores", color="Participant Group", shape="Participant Group")+
  geom_point(aes(color=speakerGuise, shape=speakerGuise), na.rm=TRUE, size=5, alpha=0.7) +
  geom_smooth(method='lm')
```

### Perception Plots
#### PropRS by Guise
##### Combined
```{r}

# Get subj means per condition
subj.means <- axb_all_data %>% 
  filter(step==0 | step==-1 | step == 1) %>%
  filter(vowel=='AU') %>%
  group_by(participantId, step, vowel, speakerGuise) %>%  summarise(mean.Prop = mean(respRS)) %>%
  mutate(step = as.factor(step))

# Get group means and se per condition (by averaging speaker means)
condition.means <- subj.means %>%
  group_by(step, vowel, speakerGuise) %>%  summarise(grandM.Prop = mean(mean.Prop), se = std.error(mean.Prop))


# Plot model predicted values
## in Proportions
au.mid.plot <- ggplot() + 
  
  # Subject observed means
  geom_jitter(aes(x=speakerGuise, y=mean.Prop, color=speakerGuise), alpha=0.3, size=3, width = 0.25, data=subj.means) +
  #geom_pointrange(aes(x=speakerGuise, y=mean.Prop, ymin=lower_subj, ymax=upper_subj, color=speakerGuise), position = position_jitter(), alpha=0.5, data=subj.means) +
  
  # Group predicted means
  geom_bar(aes(x=speakerGuise, y=grandM.Prop, fill=speakerGuise), alpha=0.5, stat="identity", position=position_dodge(), data=condition.means) + 
  geom_errorbar(aes(x=speakerGuise, y=grandM.Prop, 
                    ymin=grandM.Prop-se, ymax=grandM.Prop+se, color=speakerGuise), 
                    size=1.5, width=0.3, data=condition.means) +
  
  labs(y="Proportion RS Response", x = "Guise", color = "Guise", fill="Guise") +
  theme(plot.title = (element_text(face = "bold", hjust=0.5, size=15))) +
  coord_cartesian(ylim=c(0.0, 1.0)) +
  facet_grid(~step) +
  theme_bw() +
  scale_color_manual(values=ghibli_palette("PonyoMedium")[c(6,4,3)])+
  scale_fill_manual(values=ghibli_palette("PonyoMedium")[c(6,4,3)])+
  theme(axis.title=element_text(size=35),
        axis.text=element_text(size=30),
        strip.background =element_rect(fill="white"),
        strip.text = element_text(size=30))+
  theme(legend.title = element_text(size=30, face="bold"),
        legend.text=element_text(size=30))
au.mid.plot

ggsave(path="plots", filename="AU_ambiguous_barplot.png", au.mid.plot, width=16, height=8, units = "in" , dpi=72)


```



```{r}
# Get subj means per condition
subj.means <- axb_all_data %>% #filter(speakerGuise!='BL') %>% #filter(participantId!='5e42f74f5b772a18434cabf7') %>%
  group_by(participantId, step, vowel, speakerGuise) %>%  summarise(mean.Prop = mean(respRS))

# Get group means and se per condition (by averaging speaker means)
condition.means <- subj.means %>%
  group_by(step, vowel, speakerGuise) %>%  summarise(grandM.Prop = mean(mean.Prop), se = std.error(mean.Prop))

# Plot lineplot with error bars on step points
byGuise_prop_plot <- condition.means %>%
  ggplot(aes(x = step, y = grandM.Prop))  %>% proportion_plot_theme +
  labs(title="Raising Perception: By Guise") +
  geom_point(stat="identity", aes(colour = factor(speakerGuise)), cex=5) +
  geom_line(aes(colour=factor(speakerGuise), linetype=factor(speakerGuise)), lwd=1) +
  geom_errorbar(width = .25, aes(ymin = grandM.Prop-se, ymax = grandM.Prop+se, 
                                 colour = factor(speakerGuise))) +
  facet_grid(~vowel)

byGuise_prop_plot

### Do individual analysis of both step -1 and 1 --- those are where we found group effects
### Bayesian model averaging ---- what if anything can I generalize from these models
```

##### By Experiment
```{r}
# Get subj means per condition
subj.means <- axb_all_data %>% #filter(participantId!='5e42f74f5b772a18434cabf7') %>%
  group_by(experimentId, participantId, step, vowel, speakerGuise) %>%  summarise(mean.Prop = mean(respRS))

# Get group means and se per condition (by averaging speaker means)
condition.means <- subj.means %>%
  group_by(experimentId, step, vowel, speakerGuise) %>%  summarise(grandM.Prop = mean(mean.Prop), se = std.error(mean.Prop))

# Plot lineplot with error bars on step points
byGuise_prop_plot <- condition.means %>%
  ggplot(aes(x = step, y = grandM.Prop))  %>% proportion_plot_theme +
  labs(title="Raising Perception: By Guise") +
  geom_point(stat="identity", aes(colour = factor(speakerGuise)), cex=5) +
  geom_line(aes(colour=factor(speakerGuise), linetype=factor(speakerGuise)), lwd=1) +
  geom_errorbar(width = .25, aes(ymin = grandM.Prop-se, ymax = grandM.Prop+se, 
                                 colour = factor(speakerGuise))) +
  facet_grid(experimentId~vowel)

byGuise_prop_plot
```



#### RT by Guise
##### Combined
```{r, warning=FALSE}
# Get subj means per condition
subj.means <- axb_all_data %>% filter(speaker=='S3') %>% #filter(participantId!='5e42f74f5b772a18434cabf7') %>%
  group_by(participantId, step, vowel, speakerGuise) %>%  summarise(mean.rt = mean(log(rt)))

# Get group means and se per condition (by averaging speaker means)
condition.means <- subj.means %>%
  group_by(step, vowel, speakerGuise) %>%  summarise(grandM.rt = mean(mean.rt), se = std.error(mean.rt))

# Plot lineplot with error bars on step points
byGuise_rt_plot <- condition.means %>% 
  ggplot(aes(x = step, y = grandM.rt)) %>% guise_colors(3) +
  gg_theme() +
  labs(y = "Log Response Time", x = "Continuum Step (UR to RS)", color="Guise",
       linetype = "Guise", title="Reaction Time: By Guise") +
  geom_point(stat="identity", aes(colour = factor(speakerGuise)), cex=5) +
  geom_line(aes(colour=factor(speakerGuise), linetype=factor(speakerGuise)), lwd=1) +
  scale_linetype_manual(values=c("dotdash", "longdash", "solid")) +
  geom_errorbar(width = .25, aes(ymin = grandM.rt-se, ymax = grandM.rt+se, colour = factor(speakerGuise))) +
  facet_grid(~vowel)

byGuise_rt_plot
```

##### By Experiment
```{r, warning=FALSE}
# Get subj means per condition
subj.means <- axb_all_data %>% filter(speaker=='S3') %>% #filter(participantId!='5e42f74f5b772a18434cabf7') %>%
  group_by(experimentId, participantId, step, vowel, speakerGuise) %>%  summarise(mean.rt = mean(log(rt)))

# Get group means and se per condition (by averaging speaker means)
condition.means <- subj.means %>%
  group_by(experimentId, step, vowel, speakerGuise) %>%  summarise(grandM.rt = mean(mean.rt), se = std.error(mean.rt))

# Plot lineplot with error bars on step points
byGuise_rt_plot <- condition.means %>% 
  ggplot(aes(x = step, y = grandM.rt)) %>% guise_colors(3) +
  gg_theme() +
  labs(y = "Log Response Time", x = "Continuum Step (UR to RS)", color="Guise",
       linetype = "Guise", title="Reaction Time: By Guise") +
  geom_point(stat="identity", aes(colour = factor(speakerGuise)), cex=5) +
  geom_line(aes(colour=factor(speakerGuise), linetype=factor(speakerGuise)), lwd=1) +
  scale_linetype_manual(values=c("dotdash", "longdash", "solid")) +
  geom_errorbar(width = .25, aes(ymin = grandM.rt-se, ymax = grandM.rt+se, colour = factor(speakerGuise))) +
  facet_grid(experimentId~vowel)

byGuise_rt_plot
```

#### PropRS by Word
```{r}
# Get subj means per condition
subj.means <- axb_all_data %>% filter(speaker=="S3") %>%
  group_by(participantId, step, vowel, speakerGuise, speaker, word) %>%  summarise(mean.Prop = mean(respRS))

# Get group means and se per condition (by averaging speaker means)
condition.means <- subj.means %>%
  group_by(step, vowel, speakerGuise, speaker, word) %>%  summarise(grandM.Prop = mean(mean.Prop), se = std.error(mean.Prop))

# AI
byWord_prop_plot <- condition.means %>% filter(vowel=="AI") %>%
  ggplot(aes(x = step, y = grandM.Prop)) %>% proportion_plot_theme +
  labs(title="AI Raising Perception: By Word") +
  geom_point(stat="identity", aes(colour = factor(speakerGuise)), cex=5, alpha=0.75) +
  geom_line(aes(colour=factor(speakerGuise), linetype=factor(word)), lwd=1) +
  geom_errorbar(width = .25, aes(ymin = grandM.Prop-se, ymax = grandM.Prop+se, colour = factor(speakerGuise))) +
  facet_grid(speaker~word)
byWord_prop_plot

# AU
byWord_prop_plot <- condition.means %>% filter(vowel=="AU") %>%
  ggplot(aes(x = step, y = grandM.Prop)) %>% proportion_plot_theme +
  labs(title="AU Raising Perception: By Word") +
  geom_point(stat="identity", aes(colour = factor(speakerGuise)), cex=5, alpha=0.75) +
  geom_line(aes(colour=factor(speakerGuise), linetype=factor(word)), lwd=1) +
  geom_errorbar(width = .25, aes(ymin = grandM.Prop-se, ymax = grandM.Prop+se, colour = factor(speakerGuise))) +
  facet_grid(speaker~word)
byWord_prop_plot

```

#### PropRS by Individual (dev)
(adapted from CantoMergers project)
```{r, echo=F}
# MI guise
bySubj_prop_plot <- axb_all_data %>% filter(vowel=="AU") %>% filter(conditionId=="condA") %>%
  ggplot(aes(x=step, y=respRS, color=speakerGuise)) +
  geom_smooth(method="loess") +
  facet_wrap(~participantId) +
  geom_vline(xintercept = 0, alpha=0.5) +
  geom_hline(yintercept =  0.5, alpha = 0.5) +
  coord_cartesian(ylim=c(0, 1)) +
  scale_x_continuous(breaks = -3:3) +
  labs(title="AU Raising perception: By Participant", y="Proportion RS response", color="Guise", x="") +
  scale_color_manual(values=ghibli_palette("PonyoMedium")[c(3)])+
  gg_theme()
bySubj_prop_plot

# CN guise
bySubj_prop_plot <- axb_all_data %>% filter(vowel=="AU") %>% filter(conditionId=="condC") %>%
  ggplot(aes(x=step, y=respRS, color=speakerGuise)) +
  geom_smooth(method="loess") +
  facet_wrap(~participantId) +
  geom_vline(xintercept = 0, alpha=0.5) +
  geom_hline(yintercept =  0.5, alpha = 0.5) +
  coord_cartesian(ylim=c(0, 1)) +
  scale_x_continuous(breaks = -3:3) +
  labs(title="AU Raising perception: By Participant", y="Proportion RS response", color="Guise", x="") +
  scale_color_manual(values=ghibli_palette("PonyoMedium")[c(4)])+
  gg_theme()
bySubj_prop_plot

# BL guise
bySubj_prop_plot <- axb_all_data %>% filter(vowel=="AU") %>% filter(conditionId=="condE") %>%
  ggplot(aes(x=step, y=respRS, color=speakerGuise)) +
  geom_smooth(method="loess") +
  facet_wrap(~participantId) +
  geom_vline(xintercept = 0, alpha=0.5) +
  geom_hline(yintercept =  0.5, alpha = 0.5) +
  coord_cartesian(ylim=c(0, 1)) +
  scale_x_continuous(breaks = -3:3) +
  labs(title="AU Raising perception: By Participant", y="Proportion RS response", color="Guise", x="") +
  scale_color_manual(values=ghibli_palette("PonyoMedium")[c(2)])+
  gg_theme()
bySubj_prop_plot
```

